The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2017-12-07 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
added new figures and new FEV to presentation

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

	\end{itemize}
\item [] \textbf{Our contribution: allow in this setting the existence of an endogenous mechanism that affects future TFP}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Impulse responses to a news shock}

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
\end{figure}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Impulse responses to an IT shock}

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_47}
\end{figure}

@@

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
		\hline
	\end{tabular}
\end{large}

@@

	\item ... as well as the the conjecture that the IT shock looks similar to news along certain dimensions,

@@

@@

\item Shares of FEV of TFP explained ...
	\begin{itemize}
	\item ... are also in line with the Barsky \& Sims result ...
	\item [] For BS, news explains around 45\%, compared to 37\% here

@@

	\item ... yet suggest that the IT shock plays an important role as well
	\end{itemize}

@@

\item Check whether VAR is information-sufficient to identify the two shocks (Forni-Gambetti test)
\end{itemize}

@@

\begin{itemize}
\item Provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
\begin{itemize}
\item While the literature focuses exclusively on R\&D, we show that IT is a better variable to focus on.
\end{itemize}

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

@@

	\end{itemize}
\item [] \textbf{Our contribution: allow in this setting for the existence of an endogenous mechanism that affects future TFP}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{TFP response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_06-Dec-2017_14_00_39}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_06-Dec-2017_14_00_47}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real SP500 response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_06-Dec-2017_14_00_40}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_06-Dec-2017_14_00_48}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Other responses to  both shocks}

\begin{figure}
\begin{multicols}{2}
\centering
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_06-Dec-2017_14_00_41}\\  
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_06-Dec-2017_14_00_43}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_06-Dec-2017_14_00_44}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_06-Dec-2017_14_00_45}\\

\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_06-Dec-2017_14_00_49}\\
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_06-Dec-2017_14_00_51}\\
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_06-Dec-2017_14_00_52}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_06-Dec-2017_14_00_53}\\

\end{multicols}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
	TFP	           & 0.2060  & 0.5776 & 0.7836  \\
		\hline
	\end{tabular}
\end{large}

@@

	\item ... as well as the conjecture that the IT shock looks similar to news along certain dimensions,

@@

\vspace{0.1cm}

\item Shares of FEV of TFP explained ...
	\begin{itemize}
	\item ... also reflect the Barsky \& Sims result in that the contribution of the news shock is still significant...

	\item [] (For BS, news explains around 45\%, compared to 20\% here)

@@

	\item ... yet suggest that the IT shock plays a very important role as well (nearly 60\%)

@@

	\item ... and was previously - as anticipated by BS - partly counfounded with news!
	\end{itemize}

@@

\item Check whether VAR is information-sufficient to identify the news shock (Forni-Gambetti test) (p-val of 12\%)
\end{itemize}

@@

\begin{itemize}
\item We provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
\begin{itemize}
\item While the literature focuses exclusively on R\&D, we show that IT is a better variable to focus on.
\end{itemize}
